Introduction to VEScenarios

### 2021-05-11 sources/models/VEScenarios/tutorial_VEScenario.Rmd
final changes to VEScenario package

if(grepl('Unedited', list.files(ScenarioInputFolder, all.files = T, recursive = T))){
  stop('Please finish editing the input files before continuing. At least one is still `Unedited`.')
}

>>>>

if(any(grepl('Unedited', list.files(ScenarioInputFolder, all.files = T, recursive = T)))){
  stop('Please finish editing the input files before continuing. At least one is still `Unedited`.')
}
